Tropical methods in Lambda-Calculus

### 2023-05-13 TLLA23/BarbaPisto.tex
Mini-commit serale

 As usual, a matrix $t\in\HOM{\LREL_!}{X}{Y}$ yields a linear map $\Lawv^{!X}\to\Lawv^Y$, but we can also ``express it in the base $X$'', i.e.\ see it as a map $t^!:\Lawv^X\to\Lawv^Y$, by setting 
 $t^!(x):=t\circ_! x$.
%  (we are identifying $\Lawv^X$ with the set $\HOM{\LREL_!}{\emptyset}{X}$ of the \emph{points} of $X$).
 This is the notion of \emph{non-linear} map generated by the CCC-structure of $\LREL_!$.
 Concretely, we have $t^!(x)_b=\inf\limits_{\mu\in !X} \set{\mu x+ t_{\mu,b}}$
 where $\mu x:=\sum\limits_{a\in X} \mu(a)x_a$.
 These functions correspond then to tLs with possibly infinitely many variables (in fact, as many as the elements of $X$).

Therefore, we study in this section the properties of those functions, from the point of view of mathematical analysis.
%In the following we will also refer to them as tLs.

@@

%\begin{remark}
Notice that, by identifying $!\set{*}\simeq \N$ and $\Lawv^{\set{*}}\simeq\Lawv$, the tLs generated by the morphisms in $\HOM{\LREL_!}{\set{*}}{\set{*}}$ are exactly the functions $f:\Lawv\to\Lawv$ of shape $f(x)=\inf_{n\in\N}\set{nx+\matr f(n)}$, for some $\matr f:\N\to\Lawv$, i.e.\ usual tLs's of one variable.
In a similar way, the tropical polynomials can be identified with the tLs
$f:\Lawv^X\to\Lawv^Y$ 
 for which the support $\C F=\set{\mu\in!X\mid\matr f_{\mu,b}\neq\infty}$ is \emph{finite}, and which have thus shape $f(x)_b:=\min_{\mu\in\C F} \set{\mu x+ t_{\mu,b}}$.
 This is again the generalisation of usual tropical polynomials to the case of infinitely many variables.

>>>>

 As usual, a matrix $t\in\HOM{\LREL_!}{X}{Y}$ yields a \emph{linear} map $\Lawv^{!X}\to\Lawv^Y$, but we can also ``express it in the base $X$'' and see it as a \emph{non-linear} map $t^!:\Lawv^X\to\Lawv^Y$, by setting 
 $t^!(x):=t\circ_! x$.
%  (we are identifying $\Lawv^X$ with the set $\HOM{\LREL_!}{\emptyset}{X}$ of the \emph{points} of $X$).
% This is the notion of \emph{non-linear} map generated by the CCC-structure of $\LREL_!$.
 Concretely, we have $t^!(x)_b=\inf_{\mu\in !X} \set{\mu x+ t_{\mu,b}}$
 where $\mu x:=\sum_{a\in X} \mu(a)x_a$.
 These functions correspond then to generalised tLs, i.e.\ with possibly infinitely many variables (as many as the elements of $X$).
For $X=Y=\set{*}$, we get usual tLs of one variable.
Instead, if the support $\C F:=\set{\mu\in!X\mid\matr f_{\mu,b}\neq\infty}$ of $f$ is \emph{finite}, we get maps of shape $f(x)_b:=\min_{\mu\in\C F} \set{\mu x+ t_{\mu,b}}$, i.e.\ tropical polynomials in possibly infinitely many variables.
In this section we study the properties of generalised tLs, from the point of view of mathematical analysis.
%In the following we will also refer to them as tLs.

@@

%\begin{remark}
